Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-10-07 README.Rmd
updated to do list
changed wording from knit to compile

- Rewrite Sections 4 and 5 as needed
- Prepare for submission
- Upload the files for submission and submit

@@

## Instructions for Knitting Manuscript

When the manuscript is knit, various files will be generated (such as data-bullet-explain.rds and figure-10-1.png). The first time the manuscript is knit, it will take a while (possibly up to several hours). Once these files have been generated during the first knit, the manuscript will take much less time to knit (approximately a few minutes).

Follow these instructions to knit the manuscript:

@@

3. Knit manuscript (via the [paper.Rnw](paper.Rnw) file).

>>>>

- Final clean up and proof read of sections 4 and 5
- Prepare for submission (make sure to update date on cover letter)
- Upload the files for submission and submit

@@

## Instructions for Compiling Manuscript

When the manuscript is compiled, various files will be generated (such as data-bullet-explain.rds and figure-10-1.png). The first time the manuscript is compiled, it will take a while (possibly up to several hours). Once these files have been generated, the manuscript will take much less time to compile (approximately a few minutes).

Follow these instructions to compile the manuscript:

@@

3. Compile manuscript (via the [paper.Rnw](paper.Rnw) file).
